### 2015-05-22 writing/SNLI paper/transfer.tex
Paper update.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{2}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer}  \\
\hline
\t{SICK}            & \t{98} & \t{95} & \t{65?} & \t{68?}  \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\t{FactBank?}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{\label{tab:transferresults}
The performance of an LSTM RNN classification model on four tasks under both a random initialization and an initialization copied from a model trained on SNLI.
\todo{Fill in numbers.}}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c}
\hline
\textbf{Corpus} & \multicolumn{2}{c}{\b{Train Acc.}} &\multicolumn{3}{c}{ \b{Test Acc.}} \\
 & \t{cold start} & \t{transfer} & \t{cold start} & \t{transfer} & \t{SotA} \\
\hline
\t{SICK}            & \t{98} & \t{95} & \t{63?} & \t{69?} & \t{84.5} \\
\t{SUBJ}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?}& \t{??.?} \\
\t{SST}          & \t{??.?} & \t{??.?} & \t{43?} & \t{43?} & \t{50.6}\\
\t{FactBank?}          & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?}& \t{??.?} \\
\hline
\end{tabular}
\end{center}

\caption{\label{tab:transferresults}
The performance of an LSTM RNN classification model on four tasks under both a random initialization and an initialization copied from a model trained on SNLI. \todo{Final numbers.}}

\end{table}
..
The final column shows the state of the art results from \cite{lai2014illinois}, TODO, and \cite{tai2015improved}, respectively
...
